The problem and promise of scale in animal social multilayer networks

### 2020-02-09 paper/manuscript.Rmd
intro to perspectives

The integration of behavioural and ecological theory has shown the value of
considering the importance of scale to better understand and predict animal
social networks, including demography (Shizuka and Johnson 2019), evolutionary
and quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al.
2017), and animal personality (Sih et al. 2017). While the number of studies
integrating social network theory into a broader array of behavioural and
ecological sub-disciplines is impressive, only recently has the role of animal
space use been considered in describing the causes and consequences of the
social environment in the context of (1) phenotypes and individual fitness
(Webber & Vander Wal 2018), (2)  movement ecology and collective movement (Bode
et al. 2011), and (3) habitat selection and space use (He et al. 2019). Here, we
explore how mutlilayer networks may apply to these emerging fields to contribute
to the development of social network theory and application.

>>>>

The integration of behavioural and ecological theory has shown the value of considering 
the importance of various ecological disciplines to better understand and predict animal 
social networks, including demography (Shizuka and Johnson 2019), evolutionary and 
quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al. 2017), 
and animal personality (Sih et al. 2017). While the number of studies integrating 
social network theory into a broader array of behavioural and ecological 
sub-disciplines is impressive, only recently has the role of animal space use been 
considered in describing the causes and consequences of the social environment in the 
context of (1) phenotypes and individual fitness (Webber & Vander Wal 2018), (2) 
movement ecology and collective movement (Bode et al. 2011), and (3) habitat 
selection and space use (He et al. 2019). Importantly, much of the work linking 
space use and the social environment has been theoretical and empirical studies 
are lacking (but see Peignier et al. 2019; Pinter-Wollman 2015; Strandburg-Peshkin et al. 2015; 2017). 
Here, we discuss the role mutlilayer networks within the emerging integration 
of social and spatial ecology within the behavioural ecology literature.
